---
title: "Day 2(Summaries)"
author: "Sara"
---

## Introduction

This is the work done for day 2 where we summarized data including mpg.

## Import packages

Always place '#\| label: setup' before calling the packages.

Also, one has to install packages at the console below using : install.packages("").

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(skimr)
library(knitr)
library(kableExtra)
library(ggformula)
library(babynames)
```

## Mpg Dataset

```{r}
mpg
```

## Filtering the data(1st 10)

```{r}
mpg %>% 
  head(10)
```

## Using glimpse, mosaic, skimr and mutate to organize data

```{r}
glimpse(mpg)
```

```{r}
inspect(mpg)
```

```{r}
skimr:: skim(mpg)
```

```{r}
mpg_modified <- mpg %>%
  dplyr::mutate(
    cyl = as_factor(cyl),
    fl = as_factor(fl),
    drv = as_factor(drv),
    class = as_factor(class),
    trans = as_factor(trans)
  )
glimpse(mpg_modified)
```

## Trying with another dataset

```{r}
babynames
```

```{r}
babynames %>% filter (name == "Sara") %>% head(15)
```

## Using glimpse, mosaic, skimr and mutate to organize data

```{r}
babynames%>% mosaic::inspect()
```

```{r}
babynames %>% dplyr::glimpse()
```

```{r}
babynames_modified <- babynames %>%
  dplyr::mutate(
    sex = as_factor(sex)
  )
glimpse(babynames_modified)
```

```{r}
babynames %>% skimr::skim()
```

## Grouped for columns (using mpg dataset)

```{r}
mpg_modified %>%
  group_by(cyl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

## Grouping with cyl and fl

```{r}
mpg_modified %>%
  group_by(cyl, fl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

```{r}
mpg %>% 
  group_by(manufacturer) %>% 
  summarize(average_cty = mean(cty), count = n())
```

## Math Anxiety Data

```{r}
math_an <- read_delim("../../data/MathAnxiety.csv")
math_an
```

## Organizing Data

```{r}
math_an %>% dplyr::glimpse()
```

```{r}
math_an %>% mosaic::inspect()
```

```{r}
math_an %>% skimr::skim()
```

## Factorizing

```{r}
math_an_modified <- math_an %>%
  dplyr::mutate(
    Age = as_factor(Age),
    Gender = as_factor(Gender),
    Grade = as_factor(Grade),
  )
glimpse(math_an_modified)
```

```         
```

## Anxiety based on Gender

```{r}
math_an_modified %>%
  group_by(Gender) %>%
  summarize(average_AMAS = mean(AMAS),average_RCMAS = mean(RCMAS), count = n())
```

## Anxiety based on Age

```{r}
math_an_modified %>%
  group_by(Age) %>%
  summarize(average_AMAS = mean(AMAS),average_RCMAS = mean(RCMAS), count = n())
```

## Anxiety based on Grade

```{r}
math_an_modified %>%
  group_by(Grade) %>%
  summarize(average_AMAS = mean(AMAS),average_RCMAS = mean(RCMAS), count = n())
```

## Anxiety based on Gender & Grade

```{r}
math_an_modified %>%
  group_by(Gender, Grade) %>%
  summarize(average_AMAS = mean(AMAS),average_RCMAS = mean(RCMAS), count = n())
```
